Rule-Based Preordering on Multiple Syntactic Levels \\in Statistical Machine Translation

### 2014-11-14 Paper/paper.tex
corrected2

The decoder in phrase-based SMT systems is guided by language model, phrase table and reordering models, which makes word reordering possible. However, it may have some disadvantages, such as it can't handle long-distance reordering or unstructured reordering properly or it may be rather time-consuming.

@@

Following the analysis above, we can see the word reordering between English and Chinese is very unstructural, because it involves word movement between different word groups or syntactic hierarchies in the source language. In order to improve the reordering, we need methods that can handle more complicated, unstructural word order change. Inspired by the ideas of reordering on syntax tree and hierarchical phrases, we created the Multiple-Level-Tree(MLT) reordering, which reorders words based on multiple syntactic levels and can handle long distance word position change and complicated word position change very well.

>>>>

The decoder in phrase-based SMT systems is guided by language model, phrase table and reordering models, which makes word reordering possible. However, it may have some disadvantages, such as it can't handle long-distance reordering or unstructured reordering properly, or it may be rather time-consuming.

@@

Following the analysis above, we can see the word reordering between English and Chinese is very unstructural, because it involves word position changes between different word groups and syntactic hierarchies in the source language. In order to improve the reordering, we need methods that can handle more complicated, unstructural word order change. Inspired by the ideas of reordering on syntax tree and hierarchical phrases, we created the Multiple-Level-Tree(MLT) reordering, which reorders words based on multiple syntactic levels and can handle long distance word position change and complicated word position change very well.
